---
title: "A Cartridge Case Analysis Pipeline"
author: "Joseph Zemmels"
institute: "Center for Statistics and Applications in Forensic Evidence"
date: "2022-06-17"
output:
  xaringan::moon_reader:
    mathjax: "https://cdn.bootcss.com/mathjax/2.7.1/MathJax.js?config=TeX-MML-AM_HTMLorMML"
    css: ["default", "css/csafe.css", "css/csafe-fonts.css", "css/this-presentation.css"]
    lib_dir: libs
    nature:
      countIncrementalSlides: false
---

```{r, load_refs, include=FALSE, cache=FALSE}
library(RefManageR)
# remotes::install_github("ROpenSci/bibtex")
RefManageR::BibOptions(check.entries = FALSE,
                       bib.style = "authoryear",
                       cite.style = "alphabetic",
                       style = "markdown",
                       max.names = 1,
                       no.print.fields = c("urldate","file","issn","url","keywords","language","abstract"),
                       hyperlink = FALSE,
                       dashed = FALSE)
myBib <- RefManageR::ReadBib("ref.bib", check = FALSE)
```

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE,
        echo = FALSE,
        fig.align = 'center')
```


# Acknowledgements

## Funding statement

This work was partially funded by the Center for Statistics and Applications in Forensic Evidence (CSAFE) through Cooperative Agreement 70NANB20H019 between NIST and Iowa State University, which includes activities carried out at Carnegie Mellon University, Duke University, University of California Irvine, University of Virginia, West Virginia University, University of Pennsylvania, Swarthmore College and University of Nebraska, Lincoln.

---

# Outline

- **Introduction** Firearms and Toolmarks Identification

- **Paper \#1** A Study in Reproducibility: The Congruent Matching Cells Algorithm and cmcR package

- **Paper \#2** Diagnostic Tools for Cartridge Case Comparison Algorithms

- **Paper \#3** A Novel Cartridge Case Comparison Pipeline

- **Conclusions**

---

class: center, middle

# Introduction

## Firearms and Toolmarks Identification

---

# The Firing Process

---

# Firearms and Toolmarks Examinations


---

# Why Should F & T Examinations change?

Cite NAS, PCAST

---

class: center, middle

# Paper \#1

## A Study in Reproducibility: The Congruent Matching Cells Algorithm and cmcR package

### Submitted to the R Journal

---

# Introduction

Cite Kiegan's dissertation

---

# What we've done

---

# Modularization of Data Analysis Pipelines

- Modularization

---

# The cmcR package

- "Tidy" functionality

---

# What we need to do

- Resubmission \#2

- Cartridge case data to ISU DataShare

---

class: center, middle

# Paper \#2

## Diagnostic Tools for Cartridge Case Comparion Algorithms

### To be submitted to [...]

---

# Introduction

---

# What we've done

---

# Visual Diagnostics

---

# The `impressions` package

---

# Interactive Diagnostics

---

# cartridgeInvestigatoR

---

# What we need to do

---

class: center, middle

# Paper \#3

## A Novel Cartridge Case Comparison Pipeline

### To be submitted to [...]

---

# Introduction

- Utilize image processing and clustering algorithms to extract new features from cartridge case scans.

- Train a classifier (decision tree or random forest)

---

# What we've done

---

# Morphological Operations

- *"Some regions on the sample, such as the primer roll-off, are not informative, but may significantly affect similarity results if they are compared."* <sup>1</sup>

.footnote[[1] "Computer-Aided Firearm and Toolmark Analysis" by Johannes Soons of NIST]

- `cmcR::preProcess_erode` function

---

# DBSCAN Algorithm

- Density-Based Spatial Clustering of Applications with Noise

---

# Features based on Visual Diagnostics

---

# Train/test procedure

---

# What we need to do

- Updates to the cmcR package

  - New `preProcess_`, `comparison_`, and `decision_` functions

  - Use `caret` (Classification And REgression Training) and/or `tidymodels` R packages to implement train/test procedure `r Citep(myBib,c("caret","tidymodels"))`

- DFSC TopMatch Data Set

  - Data in Brief

  - Validation of pipeline using [\#] scans

---
class: center, middle

# Conclusions

---
class: primary-blue
# References

```{r refs1, echo=FALSE, results="asis"}
# RefManageR::NoCite(myBib,1:5)
RefManageR::PrintBibliography(myBib,start = 1,end = 6)
```

---
class: primary-blue
# References

```{r refs2, echo=FALSE, results="asis"}
# RefManageR::NoCite(myBib,1:5)
RefManageR::PrintBibliography(myBib,start = 7,end = 7)
```

